A Systematic Review of the Use of the ESM Methodology in Education

### 2020-09-14 paper_draft.Rmd
Couple small changes

---
title: "A Systematic Review of the Use of the ESM Methodology in Education"
author: "Alex Lishinski, Michael Mann, Omiya Sultana"
date: "8/5/2020"
output:
  html_document:
    df_print: paged
---

@@

# Method

>>>>

---
title: "A Systematic Review of the Use of the ESM Methodology in Education"
author: "Alex Lishinski, Michael Mann, Omiya Sultana"
date: "`r format(Sys.time(), '%B %d, %Y')`"
abstract: "This is the abstract"
output:
  html_document:
    df_print: paged
---

@@

# Methods
